---
title: "Lab 8"
author: "Muhammad Ali Valliani NetID jc8469 Section 2"
date: "November 1, 2018"
output: html_document
---

## Exercise 1

```{r}
# Loading Data
library(HistData)
velocity <- Michelson$velocity
```

```{r}
test_velocity <- t.test(velocity, mu=734.5)
test_velocity

```

Description: The Michelson's measurement data differ significantly from the current value.



## Exercise 2

```{r}
set.seed(9999)
pvals <- rep(0, 10000) # initialize vector of p-values
for(i in 1:10000) {
  x <- runif(30, min=0, max=1)
  pvals[i] <- t.test(x,mu = 0.5)$p.value
}
sum(pvals <= 0.05)
sum(pvals <= 0.05) / 10000

```

Description: The proportion created is reasonably close to 0.05 significance level.



## Exercise 3

```{r}
set.seed(9999)
pvals <- rep(0, 10000) # initialize vector of p-values
for(i in 1:10000) {
  x <- runif(2, min=0, max=1)
  pvals[i] <- t.test(x,mu = 0.5)$p.value
}
sum(pvals <= 0.05)
sum(pvals <= 0.05) / 10000
```

Description : As the sample size is 2 it won't follow CLT.


## Exercise 4

Part a

```{r}
power.t.test(n=35, delta=1.5, sd=3, sig.level=0.05, type="one.sample", alternative="two.sided")

```

Description: Increasing the alpha, decreases the probability of Beta (type 2 error).


Part b

```{r}
power.t.test(power=0.8, delta=1, sd=3, sig.level=0.05, type="one.sample", alternative = "two.sided")

```

Description: Sample size of 73 is required to dtect the difference of 1 volt.